TITLE

### 2021-10-17 paper.tex
update

\begin{subequations}
  \label{conservative-form}
  \begin{align}
   &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
   &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p\delta^{ij}\right)=0,\label{M evolution}\\
   &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
   &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=-p_{\text{cr}}\left(\frac{\partial\gamma}{\partial t} + \frac{1}{c}\partial_{j} U^{j}\right),\label{D evolution}
  \end{align}
\end{subequations}
where the five conserved quantities of gas $D$, $M^{i}$, and $\tilde{E}$ are the mass density, \
the momentum densities, and the reduced energy density, respectively. \
$\gamma$ and $U^{j}$ are the temporal and spatial component of four-velocity of gas. \
$p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density. \
$c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.

>>>>

\begin{subequations}
  \label{conservative-form}
  \begin{align}
   &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
   &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{gas}}\delta^{ij}\right)=0,\label{M evolution}\\
   &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p_{\text{gas}}\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
   &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=-p_{\text{cr}}\left(\frac{\partial\gamma}{\partial t} + \frac{1}{c}\partial_{j} U^{j}\right),\label{D evolution}
  \end{align}
\end{subequations}
where the five conserved quantities of gas $D$, $M^{i}$, and $\tilde{E}$ are the mass density, \
the momentum densities, and the reduced energy density, respectively. \
$\gamma$ and $U^{j}$ are the temporal and spatial component of four-velocity of gas. \
$p_{\text{gas}}$ is the gas pressure.\
$p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density. \
$c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation. \
Throughout this paper, Latin indices run from 1 to 3, except when stated otherwise.
